sdmTMB: an R package for fast, flexible, and user-friendly generalized linear mixed effects models with spatial and spatiotemporal random fields

### 2022-11-03 doc/paper-jss/pcod.Rmd
fix fig refs

For example, a mesh with a cutoff distance of 10 km can be made (Fig.\ \ref{fig:mesh}).

@@

Or perhaps better, use MCMC residuals (Fig.\ \ref{fig:mcmc-resids}).

>>>>

For example, a mesh with a cutoff distance of 10 km can be made (Fig.\ \ref{fig:plot-mesh}).

@@

Or perhaps better, use MCMC residuals (Fig.\ \ref{fig:mcmc-resids-vis}).
